04_DESeq_sexes

### 2019-12-23 analysis/04_LDA.Rmd
now with shape

plot_grid(a,b,c,d,e,f, nrow = 3)
```

>>>>

plot_grid(a,b,c,d,e,f, nrow = 3)

g <- ggplot(LDA.hyp, aes(x = LD1, LD2, shape = predictedstage, color = treatment)) + geom_point( ) + theme(legend.position = "none") + scale_color_manual(values = colorscharmaip)

h <- ggplot(LDA.pit, aes(x = LD1, LD2, shape = predictedstage, color = treatment)) + geom_point( ) + theme(legend.position = "none") + scale_color_manual(values = colorscharmaip)

i <- ggplot(LDA.gon, aes(x = LD1, LD2, shape = predictedstage, color = treatment)) + geom_point( ) + theme(legend.position = "none") + scale_color_manual(values = colorscharmaip)

plot_grid(g,h,i, nrow = 1)

```
